Draft Documents

### 2022-11-16 src/draft.Rmd
f3

## 3.3. Update the data set as we select variables (Isaac)
###  3.3.1. Model Fitting
###  3.3.2. Assessment
###  3.3.3. Interpretation

>>>>

## 3.3. Update the data set as we select variables (Isaac)
###  3.3.1. Model Fitting 
```{r}
df_count<-read.csv("../data/countries1.csv")
set.seed(10)
index <- sort(sample(x = nrow(df_count), size = nrow(df_count)*.8))
train <- df_count[index, ]
test <- df_count[-index, ]
```

Through forward selection, we will do feature selection. We will stop the forward selection when the adjusted r-value>0.75.

Through iteration of different models. A linear model consisting of income as a predictor has the highest adjusted r-square value=0.6201, thus it is selected.

Only some of the linear models that have been explored are showed.
```{r cars}
summary(lm(formula = pov ~ income,data = train)) #0.6201
```
Since income as a predictor brought the highest adjusted r-value, we add another predictor to income to find the predictor added to income which produced the highest adjusted r-value. reg as a predictor has the highest adjusted r-value=0.7181

```{r}
summary(lm(formula = pov ~ reg+income,data = train)) #0.7181
```

The forward selection process continues and lgdp.pc is the new predictor added that produced highest adjusted r-square=0.7492
```{r}
summary(lm(formula = pov ~ lgdp.pc+income+reg,data = train)) #0.7492
```
The addition of predictor gdp.pc produces the highest adjusted r-square value above 0.75, adjusted r-square=0.7703
```{r}
summary(lm(formula = pov ~ gdp.pc+income+reg+lgdp.pc,data = train)) #0.7703
```

Fitting of multiple linear regression with predictor gdp.pc, income, reg and lgd.pc.
```{r}
lm1<-lm(formula = pov ~ gdp.pc+income+reg+lgdp.pc,data = train)
summary(lm1)
```

###  3.3.2. Assessment
###  3.3.3. Interpretation
